Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Add more comments about why using SMT(Z3).
In Section 5.4.

\QIN{
This CCS expression composing two operators, parallel and prefix. 
It is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
That is because they are the operators conduct a similar behavior from different algebras.
}

@@

Checking satisfiability requires some symbolic computation
on the action expressions and the predicates, and this 
may depend on the specific theory of the action algebra. 
We choose to use the SMT solver Z3 as the checker engine, considering
the predicates may contain the expression 
using uninterpreted functions declared by users.
The ``Modulo Theory'' part of SMT solvers is important here, so that
the solver can use specific properties of each action algebra.

>>>>

\QIN{
This CCS expression composing two operators, parallel and prefix. In Fig.~\ref{schema:ccs-pnet}, 
it is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
That is because they are the operators conduct a similar behavior from different algebras.
}

@@

Checking satisfiability requires some symbolic computation
on the action expressions and the predicates, and this 
may depend on the specific theory of the action algebra. 
\QIN{
So we cannot do it on our own pNet API.
}

\QIN{
In our implementation, we use the SMT solver to check the predicate of the result open transitions, 
it will return whether the predicate is satisfiable or not.
}
We choose the SMT solver Z3 as the checker engine, considering
the predicates may contain the expression 
using uninterpreted functions declared by users.
The ``Modulo Theory'' part of SMT solvers is important here, so that
the solver can use specific properties of each action algebra.
